### 2021-06-09 paper/report.tex
Correct a few references.

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between May and mid-September, daily new infections
were below 20 per Million and day \citep{MaxRoser2020}. We model the
period mid-September 2020 to the end of May 2021. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) Second, a large fraction cases
during summer of 2020 were traced to international travel
\citep{KochInstitut2021,Hodcroft2021} but the precise number is difficult to model.

>>>>

We apply this model to Germany. In March and April 2020, the country broke the first
wave of the pandemic fairly quickly. Between May and mid-September, daily new infections
were below 20 per Million and day \citep{owidcoronavirus}. We model the period
mid-September 2020 to the end of May 2021. We pick the starting date for two reasons.
First, we do not include the first wave because the environment was very different
(e.g., aggregate PCR test capacity was much lower and we would require a very different
model for calculating the share of known cases) Second, a large fraction cases during
summer of 2020 were traced to international travel \citep{KochInstitut2021,Hodcroft2021}
but the precise number is difficult to model.
